---
title: "Summary analysis NeVRo"
author: "eioe" (Felx Klotzsche)
date: "17 1 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(here)
library(rstatix)
library(ggpubr)
library(grDevices)
library(ggsci) # sci color palettes
library("RColorBrewer")

# disable scientific notation:
options(scipen=999)

# Set up paths: 
path_data <- here('Results')
path_results <- here('Results')
```

## analysis accuracies:

This reads in the summaries spit out from the respective models by averaging over the folds of the CV procedure. 
```{r}
# Get summary data:
data_ls <- list()
conds <- c('mov', 'nomov')

for (cond in conds) {
  fname <- str_c('results_across_methods_', cond, '.csv')
  fpath <- file.path(path_data, fname)
  data_ls[[cond]] <- read_csv(fpath)
}

data_df <- bind_rows(data_ls, .id = 'Condition')

# select data of binary approaches only and put into long format:
data_bin <- data_df %>% 
  dplyr::rename("Condition" = "Condition") %>% 
  select(Condition, Subject, LSTM, CSP) %>% 
  gather('LSTM', 'CSP', key = Model, value = Accuracy)

data_bin_summary <- data_bin %>% 
  group_by(Condition, Model) %>% 
  summarise(meanAccuracy = mean(Accuracy, na.rm = TRUE)) 
data_bin_summary
```


Now we read in the data from the single samples/epochs/seconds. Namely their actual ratings (= labels, ground truth) and the binary predictions of each model:
```{r message=FALSE, warning=FALSE}

#Get single sample data:

model_pred_ls <- list()
model_targ_ls <- list()
model_prob_ls <- list()

data_pred_ls <- list()
data_targ_ls <- list()
data_prob_ls <- list()

data_pred_df <- NULL
data_targ_df <- NULL
data_pred_df <- NULL

samp_col_names <- sprintf('S%d', 1:270)

for (model in list('CSP', 'LSTM')) {

  for (cond in conds) {
    # Get prediction data:
    fname <- str_c('predictionTable', model, '_', cond, '.csv')
    fpath <- file.path(path_data, model, cond, fname)
    dat <- read_csv(fpath, col_names = FALSE, na = c("", "NaN"))
    # Recode CSP data to [-1,1]:
    if (model == 'CSP') {
      dat <- dat %>% 
        mutate_at(vars(X2:X271), as.numeric) %>% 
         mutate_at(vars(X2:X271), list(~recode(.,`0` = -1)))
    }
    data_pred_ls[[cond]] <- dat
    dat <- NULL # better be sure
    
    # Get target data:
    fname <- str_c('targetTable', model, '_', cond, '.csv')
    fpath <- file.path(path_data, model, cond, fname)
    dat <- read_csv(fpath, col_names = FALSE, na = c("", "NaN"))
    # Recode CSP data to [-1,1]:
    if (model == 'CSP') {
      dat <- dat %>% 
        mutate_at(vars(X2:X271), as.numeric) %>% 
         mutate_at(vars(X2:X271), list(~recode(.,`1` = -1, `2`= 1)))
    }
    data_targ_ls[[cond]] <- dat
    dat <- NULL
    
    # Get probability data:
    fname <- str_c('predictionTableProbabilities', model, '_', cond, '.csv')
    fpath <- file.path(path_data, model, cond, fname)
    dat <- read_csv(fpath, col_names = FALSE, na = c("", "NaN"))
    data_prob_ls[[cond]] <- dat
    dat <- NULL
  }
  
  data_pred_df <- bind_rows(data_pred_ls, .id = 'condition') %>% 
    rename_all(~c('Condition', 'Subject', samp_col_names))
  data_targ_df <- bind_rows(data_targ_ls, .id = 'condition') %>% 
    rename_all(~c('Condition', 'Subject', samp_col_names))
  data_prob_df <- bind_rows(data_prob_ls, .id = 'condition') %>% 
    rename_all(~c('Condition', 'Subject', samp_col_names))
  
  
  model_pred_ls[[model]] <- data_pred_df
  model_targ_ls[[model]] <- data_targ_df
  model_prob_ls[[model]] <- data_prob_df
}

data_pred_df_full <- bind_rows(model_pred_ls, .id = 'Model') 
data_targ_df_full <- bind_rows(model_targ_ls, .id = 'Model') 
data_prob_df_full <- bind_rows(model_prob_ls, .id = 'Model')
```


Now we have 3 big data frames:  
- Target (behavioral ratings, ground truth)  
- Model Prediction (binary) 
- Preiction probability  



```{r}
# combine, calc accuracy, and run binomial test:

binom_func <- function(n_corr_samps, n_samps_tot, p_guess) {
  binom.test(n_corr_samps, n_samps_tot, p = p_guess, alternative = "two.sided")
}

# Compare preditions to target:
pred_success <- data_pred_df_full
pred_success[, samp_col_names] <- data_targ_df_full[, samp_col_names] ==
  data_pred_df_full[, samp_col_names]

# Calculate accuracy & run bionomial test on single subjects:
pred_success %>% 
  mutate(Ncorrect = rowSums(select(., samp_col_names), na.rm = T), 
         Ntot = rowSums(!is.na(select(., samp_col_names))), 
         accuracy = Ncorrect/Ntot) %>% 
  rowwise() %>% 
  mutate(p_val = binom_func(Ncorrect, Ntot, 0.5)$p.value) %>% 
  select(-one_of(samp_col_names)) -> pred_success

# summary stats:
pred_success %>% 
  mutate(pval_sign = p_val < 0.05, acc_imp = round(accuracy,1)) %>% 
  group_by(Model, Condition) %>% 
  summarise(n = n(),
            Ncorr_median = median(Ncorrect), 
            Ntot_median = median(Ntot),
            mean_accuracy = mean(accuracy),
            sd_accuracy = sd(accuracy),
            se_accuracy = sd(accuracy)/sqrt(n),
            min_accuracy = min(accuracy), 
            max_accuracy = max(accuracy),
            n_sig_pval = sum(pval_sign)) %>% 
  mutate(prop_sign_pval = n_sig_pval/n)  -> accuracy_summary

print(accuracy_summary)

# Run t tests against chance level:
pwc <- pred_success %>%
  #filter(Model == mod) %>% 
  group_by(Model, Condition) %>% 
  summarise(t     = t.test(accuracy, mu = 0.5)$statistic, 
            p_val = t.test(accuracy, mu = 0.5)$p.value, 
            df    = t.test(accuracy, mu = 0.5)$parameter)
print(pwc)

## Write out result tables:
fpath <- file.path(path_results, 'Stats', 'results_binomTest_allsubjects.csv')
write_csv2(pred_success, fpath)

fpath <- file.path(path_results, 'Stats', 'results_binomTest_summary.csv')
write_csv2(accuracy_summary, fpath)

```


To further compare, we can now put the accuracies into an ANOVA:
```{r}

pred_success_completecases <- pred_success %>% 
  group_by(Subject) %>% 
  mutate(n = n()) %>% 
  filter(n == 4) %>%   #only use full cases (data for both conditions) 
  mutate(Model = as_factor(Model), 
         Condition = as_factor(Condition))

aov.acc <- aov(accuracy ~ Model * Condition + Error(Subject/(Model * Condition)),
               data = pred_success_completecases)

summary(aov.acc)

```



```{r, include=F}



coll <- list()
varas <- rep(0,45)
means <- rep(0,45)

for (i in 1:45) {
  pred_probs <- data_prob_df_full %>% 
    slice(i) %>% 
    pivot_longer(samp_col_names) %>% 
    drop_na()
  labels <- data_targ_df_full %>% 
    filter(Model == 'CSP') %>% # Remove this line once LSTM data is there
    slice(i) %>% 
    pivot_longer(samp_col_names) %>% 
    drop_na()
  
  #pred <- prediction(pred_probs$value, 
  #                   labels$value)
  #perf <- performance(pred, "auc")
  
  #coll[[i]] <- perf@y.values
    
  #cat(i, ' --- ', perf@y.values[[1]], '\n')
  
  #pp <- perf@y.values[[1]]
  #vara <- ((pp *(1-pp)) + (90-1)*(pp/(2-pp)-pp^2) + (90-1)*(2*pp^2/(1+pp)))/(90^2)
  
  # varas[i] <- vara
  # means[i] <- pp
  # 
  # zz <- (pp-0.5)/sqrt(vara)
  # cat(i, ' --- ', zz, '\n')
  # 
  # perf <- performance(pred, "tpr", "fpr")
  # 
  # cc <- ifelse(zz>1.6, 'green', 'red')
  # if (i==1) {
  #     plot(perf, lwd = 0.01, col = cc)
  # } else {
  #   
  #   lines(as_vector(perf@y.values) ~ as_vector(perf@x.values), 
  #         lwd = 0.01, 
  #         col = cc)
  # }
  # lines(0:1, 0:1, lwd = 3)

}
```


### Plot the results:

Plot accuracies for both binary approaches per movement condition (ordered by CSP accuracy):
```{r, include=FALSE}
# 
# # Plot histograms/freqpolys:
# ggplot(pred_success, aes(accuracy, linetype = Condition)) +
#   geom_freqpoly(binwidth = 0.03) + scale_color_brewer(palette="Paired") + 
#   theme_bw() + facet_wrap(~Model, scales = 'free')
# 
# 
# ggplot(data_df, aes(SPOC_LAMBDA, linetype = condition)) + 
#   geom_freqpoly(binwidth = 0.3)
# 
# pred_success %>% 
#   rownames_to_column() %>% 
#   arrange(Model, Condition, accuracy) %>%
#   mutate(mixed = as.integer(rowname)) %>% 
#   select(-rowname) %>% 
#   rownames_to_column()  %>% 
#   arrange(mixed) -> ordered_subs
# ordervar<- rep(as.integer(ordered_subs$rowname[1:45]), 2)
# 
# pred_success %>%
#   add_column(ordervar) %>% 
#   mutate(Condition = recode(Condition, mov = 'Movement', nomov = 'No Movement'))  %>% 
#   arrange(ordervar) %>% 
#   ggplot(aes(x = ordervar, y = accuracy, col = Model)) + 
#   facet_wrap(~Condition, scales = 'free') +
#   geom_point(aes(shape = Model), size = 3) +
#   theme_bw() + 
#   scale_color_brewer(palette="Paired") +
#   scale_shape_manual(values=c(13, 16, 17)) + 
#   xlab('Subjects') + 
#   theme(axis.text.x=element_blank()) 
```


Plot accuracies of the two binary approaches against each other (per movement condition):
```{r}
# 
# ## Create corr plot across conditions and methods:
# 
# data_df <- data_df %>% 
#   mutate(Condition = condition) 
# 
# p1 <- pred_success %>%
#   mutate(Condition = recode(Condition, mov = 'Movement', nomov = 'No Movement'))  %>% 
#   select(Condition, Subject, Model, accuracy) %>% 
#   spread(Model, accuracy) %>% 
#   left_join(data_df[, c("Condition", "Subject", "SPOC_LAMBDA")], by = c("Condition", "Subject"))  %>% 
#   ggplot(aes(x = CSP, y = LSTM)) + 
#   facet_wrap(~Condition, scales = 'free') +
#   geom_point(size = 1, color = 'darkblue') +
#   stat_smooth(aes(y = LSTM), method = 'lm', size = 0.2, alpha = 0.1, xmax = 0, color = 'darkblue') +
#   #stat_smooth(aes(y = SPOC_LAMBDA * -1), method = 'lm', size = 0.2, alpha = 0.1, xmax = 0, color = 'green') +
#   theme_bw() + 
#   theme(axis.title.x = element_blank()) +
#   scale_color_brewer(palette="Paired") +
#   scale_shape_manual(values=c(13, 16, 17)) + 
#   xlab('accuracy CSP') + 
#   ylab('accuracy LSTM') + 
#   #ylim(c(0.449, 0.77)) + 
#   xlim(c(0.449, 0.77)) 
# 
# p2 <- pred_success %>%
#   #mutate(Condition = recode(Condition, mov = 'Movement', nomov = 'No Movement'))  %>% 
#   select(Condition, Subject, Model, accuracy) %>% 
#   spread(Model, accuracy) %>% 
#   left_join(data_df[, c("Condition", "Subject", "SPOC_LAMBDA")], by = c("Condition", "Subject"))  %>% 
#   ggplot(aes(x = CSP, y = SPOC_LAMBDA)) + 
#   facet_wrap(~Condition, scales = 'free', labeller = ) +
#   geom_point(size = 1, color = 'darkgreen') +
#   stat_smooth(method = 'lm', size = 0.2, alpha = 0.1, xmax = 0, color = 'darkgreen') + 
#   theme_bw() + theme(strip.text.x = element_blank()) + 
#   scale_color_brewer(palette="Paired") +
#   scale_shape_manual(values=c(13, 16, 17)) + 
#   xlab('accuracy CSP') + 
#   ylab('lambda SPoC') + 
#   ylim(c(-1.7, 0.3)) + 
#   xlim(c(0.449, 0.77)) 
# 
# p3 <- pred_success %>%
#   #mutate(Condition = recode(Condition, mov = 'Movement', nomov = 'No Movement'))  %>% 
#   select(Condition, Subject, Model, accuracy) %>% 
#   spread(Model, accuracy) %>% 
#   left_join(data_df[, c("Condition", "Subject", "SPOC_LAMBDA")], by = c("Condition", "Subject"))  %>% 
#   ggplot(aes(x = LSTM, y = SPOC_LAMBDA)) + 
#   facet_wrap(~Condition, scales = 'free', labeller = ) +
#   geom_point(size = 1, color = 'darkred') +
#   stat_smooth(method = 'lm', size = 0.2, alpha = 0.1, xmax = 0, color = 'darkred') + 
#   theme_bw() + theme(strip.text.x = element_blank()) + 
#   scale_color_brewer(palette="Paired") +
#   scale_shape_manual(values=c(13, 16, 17)) + 
#   xlab('accuracy LSTM') + 
#   ylab('lambda SPoC') + 
#   ylim(c(-1.7, 0.3)) + 
#   xlim(c(0.449, 0.77)) 
# 
# 
# 
# ggarrange(p1,p2,p3, 
#           #labels = c("A", "B"),
#           ncol = 1, nrow = 3)


```

```{r}
## Create corr plot across conditions and methods:
## (fancy version): 


data_acc <- pred_success %>%
  select(Condition, Subject, Model, accuracy) %>% 
  spread(Model, accuracy) %>% 
  left_join(data_df[, c("Condition", "Subject", "SPOC_LAMBDA", "SPOC_CORR")], by = c("Condition", "Subject")) %>% 
  mutate(SPoC = SPOC_CORR)

models_l <- c('SPoC', 'CSP', 'LSTM')
lims_l <- list(SPoC = c(-0.70, 0.25), 
               # Use c(-0.7, 0.25) for SPOC_CORR and c(-1.7, 0.25) for SPOC_LAMBDA 
               CSP = c(0.44, 0.8), 
               LSTM = c(0.44, 0.8))
cols_l <- list()
for (i in 1:3) {
  cols_l[[i]] <- list()
  for (j in 1:3) {
    cols_l[[i]][[j]] <- "black"
  }
}


# Color coding :
cols_paired <- brewer.pal(12, "Paired")

cols_cond <- list(mov = cols_paired[[1]], 
                  nomov = cols_paired[[11]])

cols_l[[1]][[2]] <- cols_paired[[4]]
cols_l[[1]][[3]] <- cols_paired[[6]]
cols_l[[2]][[3]] <- cols_paired[[8]]


pplots <- list()
pplots[[1]] = list()
pplots[[2]] = list()
pplots[[3]] = list()

for (i in 1:3) {
  for (j in 1:3 ) {
    
      color_ <- cols_l[[min(i,j)]][[max(i,j)]]
      ylims_ <- lims_l[[models_l[i]]]
      xlims_ <- lims_l[[models_l[j]]]
      range_x <- xlims_[2] - xlims_[1]
      range_y <- ylims_[2] - ylims_[1]
      relation_xy <- range_x / range_y
    
    if (i == 3) {
          x_lab <- element_text(size = rel(1.5), angle = 0)
          x_ticks <- element_text()
        } else {
          x_lab <- element_blank()
          x_ticks <- element_blank()
        }
        if (j == 1) {
          y_lab <- element_text(size = rel(1.5), angle = 90)
          y_ticks <- element_text()
        } else {
          y_lab <- element_blank()
          y_ticks <- element_blank()
        }
    
    if (! (i == j)) {
      cat("Doing ", models_l[i], " ~ ", models_l[j], "\n")
      cond_ <- ifelse(i < j, 'nomov', 'mov')
      #x_lab <- ifelse(i == 3, element_text(size = rel(1.5), angle = 90), xx)
      #y_lab <- ifelse(i == 3, element_text(size = rel(1.5), angle = 90), element_blank())

      
      pplots[[i]][[j]] <- local({
        i <- i
        j <- j
        
        # Calculate correlation info:
        cordat <- data_acc %>% 
          filter(Condition == cond_)  
        v1 <- as_vector(cordat[, models_l[i]])
        v2 <- as_vector(cordat[, models_l[j]])
        cor.res <- cor.test(v1, v2, method = 'pearson')
        cor.res <- tidy(cor.res)
        txt_estim <- paste0("italic(r)(",cor.res$parameter,") ==", round(cor.res$estimate, 2))
        pval <- round(cor.res$p.value, 3)
        pval_sign <- ifelse(pval == 0, '<', '==')
        pval_formatted <- str_remove(ifelse(pval == 0, 0.001, pval), '0')
        txt_pval <- sprintf('italic(p) %s "%s"', pval_sign, pval_formatted)
        #txt_pval <- "paste(italic(R) ^ 2, \" = .75\")"

        pp <- data_acc %>% 
          filter(Condition == cond_) %>% 
          ggplot(aes(x = get(models_l[j]), y = get(models_l[i]))) +
          #facet_wrap(~Condition, scales = 'free', labeller = ) +
          
          # Print colored boxes for condition axis labels: 
          annotate(geom = "polygon", 
                   x = c(min(xlims_) - 0.06 * (xlims_[2] - xlims_[1]), 
                         max(xlims_) + 1, 
                         max(xlims_) + 1, 
                         min(xlims_) + 0.06 * (xlims_[2] - xlims_[1])), 
                   y = c(min(ylims_)- 0.06 * abs(min(ylims_)), 
                         min(ylims_)- 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 0.06 * abs(min(ylims_))), 
                   fill = cols_cond[[cond_]], 
                   alpha = 0.8) + 
          annotate(geom = "polygon",
                   x = c(min(xlims_) - 0.06 * (xlims_[2] - xlims_[1]), 
                         min(xlims_) + 0.06 * (xlims_[2] - xlims_[1]), 
                         min(xlims_) + 0.06 * (xlims_[2] - xlims_[1]), 
                         min(xlims_) - 0.06 * (xlims_[2] - xlims_[1])), 
                   y = c(min(ylims_)- 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 10 * abs(min(ylims_)),
                         min(ylims_)+ 10 * abs(min(ylims_))), 
                   fill = cols_cond[[cond_]], 
                   alpha = 0.8) + 
          
          #Print cond axis labels:
          annotate(geom = "text", 
                   label = cond_,
                   #fontface = 'italic',
                   x = mean(xlims_),
                   y = min(ylims_) + 0.02 * abs(min(ylims_)), 
                   size = 3) +
          annotate(geom = "text", 
                   label = cond_,
                   #fontface = 'italic',
                   x = min(xlims_),
                   y = mean(ylims_), 
                   size = 3, 
                   angle = 90) +        
          
          
          annotate(geom = 'text', 
                   label = c(txt_estim, txt_pval),
                   parse = TRUE, 
                   size = 2.5,
                   x = min(xlims_) + (max(xlims_) - min(xlims_)) * 0.1,
                   y = c(max(ylims_) - (max(ylims_) - min(ylims_)) * 0.05, 
                         max(ylims_) - (max(ylims_) - min(ylims_)) * 0.1), 
                   hjust = 'left') +
          
          geom_point(size = 1, color = color_) +
          stat_smooth(method = 'lm', size = 0.2, alpha = 0.1, xmax = 0, color = color_) + 
          
          xlab(models_l[j]) +
          ylab(models_l[i]) + 
          theme_bw() + 
          theme(strip.text.x = element_blank(), 
                axis.title.x = x_lab, 
                axis.title.y = y_lab, 
                axis.text.x = x_ticks,
                axis.text.y = y_ticks,
                aspect.ratio = 1, 
                plot.margin = unit(c(0.03, 0.3, 0.03, 0.3)*0.2, "cm")) +
          coord_cartesian(xlim = lims_l[[models_l[j]]], 
                          ylim = lims_l[[models_l[i]]])+
        
          #ylab(models_l[i])
          #xlab('accuracy CSP') + 
          #ylab('lambda SPoC') #+ 
          #ylim(ylims_) + 
          #xlim(xlims_) 
          coord_cartesian(xlim = lims_l[[models_l[j]]], 
                  ylim = lims_l[[models_l[i]]])
        
        print(pp)
      })
    
    } else {
      pplots[[i]][[j]] <- local({
        i <- i
        j <- j
        xlims_ <- xlims_
        ylims_ <- ylims_
        
        
        # Calculate correlation info:
        cordat <- data_acc %>% 
          pivot_wider(id_cols = Subject, names_from = Condition, values_from = models_l[i])  
        v1 <- as_vector(cordat[, 'mov'])
        v2 <- as_vector(cordat[, 'nomov'])
        cor.res <- cor.test(v1, v2, method = 'pearson')
        cor.res <- tidy(cor.res)
        txt_estim <- paste0("italic(r)(",cor.res$parameter,") ==", round(cor.res$estimate, 2))
        pval <- round(cor.res$p.value, 3)
        pval_sign <- ifelse(pval == 0, '<', '==')
        pval_formatted <- str_remove(ifelse(pval == 0, 0.001, pval), '0')
        txt_pval <- sprintf('italic(p) %s "%s"', pval_sign, pval_formatted) 
        
        
        pp <- data_acc %>% 
          select(Subject, Condition, models_l[i]) %>% 
          pivot_wider(id_cols = Subject, 
                      names_from = Condition, 
                      values_from = models_l[i]) %>%  
          ggplot(aes(x = nomov, y = mov)) + 
          geom_point(aes(x=xlims_[1], y = ylims_[1])) +
          
          # Print colored boxes for condition axis labels: 
          annotate(geom = "polygon", 
                   x = c(min(xlims_) - 0.06 * (xlims_[2] - xlims_[1]), 
                         max(xlims_) + 1, 
                         max(xlims_) + 1, 
                         min(xlims_) + 0.06 * (xlims_[2] - xlims_[1])), 
                   y = c(min(ylims_)- 0.06 * abs(min(ylims_)), 
                         min(ylims_)- 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 0.06 * abs(min(ylims_))), 
                   fill = cols_cond[['nomov']], 
                   alpha = 0.8) + 
          annotate(geom = "polygon",
                   x = c(min(xlims_) - 0.06 * (xlims_[2] - xlims_[1]), 
                         min(xlims_) + 0.06 * (xlims_[2] - xlims_[1]), 
                         min(xlims_) + 0.06 * (xlims_[2] - xlims_[1]), 
                         min(xlims_) - 0.06 * (xlims_[2] - xlims_[1])), 
                   y = c(min(ylims_)- 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 0.06 * abs(min(ylims_)), 
                         min(ylims_)+ 10 * abs(min(ylims_)),
                         min(ylims_)+ 10 * abs(min(ylims_))), 
                   fill = cols_cond[['mov']], 
                   alpha = 0.8) + 
          
          # Print condition axis labels: 
          annotate(geom = "text", 
                   label = 'nomov',
                   #fontface = 'italic',
                   x = mean(xlims_),
                   y = min(ylims_)+ 0.02 * abs(min(ylims_)), 
                   size = 3) +
          annotate(geom = "text", 
                   label = 'mov',
                   #fontface = 'italic',
                   x = min(xlims_),
                   y = mean(ylims_), 
                   size = 3, 
                   angle = 90) + 
          
          annotate(geom = 'text', 
                   label = c(txt_estim, txt_pval),
                   parse = TRUE, 
                   size = 2.5,
                   x = min(xlims_) + (max(xlims_) - min(xlims_)) * 0.1,
                   y = c(max(ylims_) - (max(ylims_) - min(ylims_)) * 0.05, 
                         max(ylims_) - (max(ylims_) - min(ylims_)) * 0.1), 
                   hjust = 'left') + 
          
          geom_point(size = 1, color = 'black') +
          stat_smooth(method = 'lm', size = 0.2, alpha = 0.1, color = 'black') + 
          
          theme_bw() + 
          theme(strip.text.x = element_blank(), 
                axis.title.x = x_lab, 
                axis.title.y = y_lab, 
                axis.text.x = x_ticks,
                axis.text.y = y_ticks,
                aspect.ratio = 1, 
                plot.margin = unit(c(0.03, 0.3, 0.03, 0.3)*0.2, "cm")) +
          scale_fill_jco() + 
          #ylim(lims_l[[models_l[i]]]) + 
          #xlim(lims_l[[models_l[j]]]) +
          coord_cartesian(lims_l[[models_l[i]]], lims_l[[models_l[i]]]) + 
          xlab(models_l[i]) +
          ylab(models_l[j])
          
        
        print(pp)
          
      })
    }
  }
}


fig <- ggarrange(
          pplots[[1]][[1]],
          pplots[[1]][[2]], 
          pplots[[1]][[3]], 
          pplots[[2]][[1]], 
          pplots[[2]][[2]], 
          pplots[[2]][[3]], 
          pplots[[3]][[1]], 
          pplots[[3]][[2]], 
          pplots[[3]][[3]], 
          ncol = 3, 
          nrow = 3, 
          label.x = c(0.5, 0.5, 0.5), 
          hjust = 0.5, 
          vjust = 10, 
          align = 'hv')#, 
          #heights = c(1,1,1.32), 
          #widths =  c(1))
          

fig
ggsave(file="C:/Users/Felix/Downloads/pp_cor_0409.svg", plot=fig, width=8, height=8)


# annotate_figure(fig,
#                 top = text_grob("Visualizing len", color = "red", face = "bold", size = 14),
#                 bottom = text_grob(c("hans", "SPoC CSP LSTM"), color = c("red", "blue"), hjust = c(-12, 0)),
#                                     #face = "italic", size = 10),
#                 left = text_grob("Tooth length", color = "green", rot = 90),
#                 right = "I'm done, thanks :-)!",
#                 fig.lab = "Figure 1", fig.lab.face = "bold"
#)
```

```{r}
pp <- pplots[[i]][[j]] + 
  annotate(geom = "polygon", 
                   x = c(min(xlims_) - 0.05 * (xlims_[2] - xlims_[1]), 
                         max(xlims_) + 1, 
                         max(xlims_) + 1, 
                         min(xlims_) + 0.05 * (xlims_[2] - xlims_[1])), 
                   y = c(min(ylims_)- 0.04 * abs(min(ylims_)), 
                         min(ylims_)- 0.04 * abs(min(ylims_)), 
                         min(ylims_)+ 0.04 * abs(min(ylims_)), 
                         min(ylims_)+ 0.04 * abs(min(ylims_))), 
           fill = 'red', 
           alpha = 0.1) + 
  annotate(geom = "polygon",
           x = c(min(xlims_) - 0.05 * (xlims_[2] - xlims_[1]), 
                 min(xlims_) + 0.05 * (xlims_[2] - xlims_[1]), 
                 min(xlims_) + 0.05 * (xlims_[2] - xlims_[1]), 
                 min(xlims_) - 0.05 * (xlims_[2] - xlims_[1])), 
           y = c(min(ylims_)- 0.04 * abs(min(ylims_)), 
                 min(ylims_)+ 0.04 * abs(min(ylims_)), 
                 min(ylims_)+ 10 * abs(min(ylims_)),
                 min(ylims_)+ 10 * abs(min(ylims_))), 
           fill = 'blue', 
           alpha = 0.1) + 
          annotate(geom = "text", 
                   label = 'mov',
                   fontface = 'italic',
                   x = min(xlims_),
                   y = mean(ylims_), 
                   size = 3, 
                   angle = 90) + 
  # ylim(lims_l[[models_l[i]]]) + 
  # xlim(lims_l[[models_l[j]]]) 
  coord_cartesian(xlim = lims_l[[models_l[j]]], 
                  ylim = lims_l[[models_l[i]]])
    
pp
```




Plot the accuracies in the two movement conditions against each other (per model) to see whether there were subject specific trends:
```{r}
pred_success %>%
  mutate(Condition = recode(Condition, mov = 'Movement', nomov = 'NoMovement'))  %>% 
  select(Condition, Subject, Model, accuracy) %>% 
  spread(Condition, accuracy) %>% 
  ggplot(aes(x = Movement, y = NoMovement)) +
  facet_wrap(~Model, scales = 'free') +
  geom_point(aes(shape = Model), size = 3, color = 'darkblue') +
  stat_smooth(method = 'lm', size = 0.2, alpha = 0.1) +
  theme_bw() + 
  scale_color_brewer(palette="Paired") +
  scale_shape_manual(values=c(13, 16, 17)) + 
  xlab('Movement') + 
  ylab('No Movement') + 
  ylim(c(0.449, 0.71)) + 
  xlim(c(0.449, 0.71)) 



# check correlation:
summary(lm(pred_success$accuracy[1:45]~pred_success$accuracy[46:90]))
```


```{r}
######## old stuff (can probably be deprecated):

# 
# data_bin %>% 
#   select(accuracy) %>% 
#   na.omit() %>% 
#   mutate(avg_n_corr_samples = round(accuracy * 180)) %>% 
#   rowwise() %>% 
#   mutate(p_val = binom_func(avg_n_corr_samples, 180, 0.5)$p.value) -> he
#   
# 
# 
# 
# dat %>% 
#   select(condition, Subject, LSTM, CSP) %>% 
#   gather('LSTM', 'CSP', key = method, value = accuracy) %>% 
#   group_by(method, condition) %>% 
#   summarise(meanacc = mean(accuracy, na.rm=T)) ->
#   outp
# 
# 

```


